|

### 2023-06-02 manuscript/paper.Rmd
Fix notation mistake in priors.
Updated affiliations

---
title: |
  |  \Large Increased sexual dimorphism evolves in a fossil stickleback following ecological release from fish piscivores
author: | 
  | \large Allison Ozark$^1$, Akhil Ghosh$^1$, Raheyma Siddiqui$^1$, Matthew Stuart$^1$,
  | \large  Samantha Swank$^1$, Michael A. Bell$^2$, Gregory J. Matthews$^1$, and Yoel E. Stuart$^1$ \vspace{-1.1mm}
  |
  | \large $^1$ Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  |
  | \large $^2$ University of California Museum of Paleontology, Berkeley, CA, USA \vspace{-1.1mm}
  |
abstract: |
  | Everyone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

@@

\begin{align}
\sigma_k & \iid \mathcal{N}(0,100)I_{\{\sigma > 0\}} \nonumber \\
\tau_k & \iid \mathcal{N}(0,100)I_{\{\tau > 0\}} \nonumber \\
\kappa_k & \iid \mathcal{N}(0,1)I_{\{-1 < \kappa_g < 1\}} \nonumber \\
\beta_k & \iid \mathcal{N}(0,5) \\
\theta_{k,g} & \iid \mathcal{N}(0,10000)
\omega_l & \iid \mathcal{N}(0,100)I_{\{\tau > 0\}} \nonumber \\
\phi_l & \iid \mathcal{N}(0,1)I_{\{-1 < \kappa_g < 1\}} \nonumber \\
\gamma_{l,g} & \iid \mathcal{N}(0,10000)
\label{eq:priors}
\end{align}

>>>>

---
title: |
  |  \Large Increased sexual dimorphism evolves in a fossil stickleback following ecological release from fish piscivores
author: | 
  | \large Allison Ozark$^1$, Akhil Ghosh$^2$, Raheyma Siddiqui$^1$, Matthew Stuart$^{2,3}$,
  | \large  Samantha Swank$^1$, Michael A. Bell$^4$, Gregory J. Matthews$^{2,3}$, and Yoel E. Stuart$^1$ \vspace{-1.1mm}
  |
  | \large $^1$ Department of Biology, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  |
  | \large $^2$ Department of Mathematics and Statistics, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  |  
  | \large $^3$ Center for Data Science and Consulting, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  |  
  | \large $^4$ University of California Museum of Paleontology, Berkeley, CA, USA \vspace{-1.1mm}
  |
abstract: |
  | Everyone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

@@

\begin{align}
\sigma_k & \iid \mathcal{N}(0,100)I_{\{\sigma > 0\}} \nonumber \\
\tau_k & \iid \mathcal{N}(0,100)I_{\{\tau > 0\}} \nonumber \\
\kappa_k & \iid \mathcal{N}(0,1)I_{\{-1 < \kappa_g < 1\}} \nonumber \\
\beta_k & \iid \mathcal{N}(0,5) \nonumber \\
\theta_{k,g} & \iid \mathcal{N}(0,10000) \nonumber \\
\omega_l & \iid \mathcal{N}(0,100)I_{\{\tau > 0\}} \nonumber \\
\phi_l & \iid \mathcal{N}(0,1)I_{\{-1 < \kappa_g < 1\}} \nonumber \\
\gamma_{l,g} & \iid \mathcal{N}(0,10000)
\label{eq:priors}
\end{align}
